Using numerical modelling to investigate temperature and wave exposure as drivers

### 2019-08-29 morphology_paper.Rmd
tiny change in statistical methods section

Characterisation of morphological characteristics in relation to temperature and wave exposure non-parametric statistical methods were used. Morphological characteristics were categorised according to temperature regime and wave exposure category for each each species and population of kelp in this study. Significant differences between temperatre regime and wave exposure categories were tested with wilcox tests. Notched boxplots allowed comparison between individual categories of wave exposure. In order to investigate specific drivers of morphological characteristics a distance-based redundancy analysis was performed using the *rda* function in the *vegan* software package [@Oksanen2015-vj] in R (R Core Team, 2019). The abiotic data covered all study sites for both species of kelp. Both morphology and abiotic data (temperature, waves and wind) were standardised using the *decostand* function in the *vegan* software package; morphology data were used as response variables and the abiotic data as explanatory variables. To determine the explanatory variables that best describe patterns in the response data, a full RDA was performed using a complete set of explanatory variables. Forward selection was then used to reduce the number of explanatory variables as well as prevent the inflation of overall type I error. To further improve the model, pairwise coefficients and Variance Inflation Factor (VIF) were calculated to identify variables with high multicollinearity. The computation of the parsimonious RDA was followed by permutation tests of the adjusted *R*2 to assess significance of constraints.

>>>>

Characterisation of morphological characteristics in relation to temperature and wave exposure non-parametric statistical methods were used. Morphological characteristics were categorised according to temperature regime and wave exposure category for each each species and population of kelp in this study. Significant differences between temperatre regime and wave exposure categories were tested with wilcox tests and notched boxplots allowed comparison between individual categories of wave exposure. In order to investigate specific drivers of morphological characteristics a distance-based redundancy analysis was performed using the *rda* function in the *vegan* software package [@Oksanen2015-vj] in R (R Core Team, 2019). The abiotic data covered all study sites for both species of kelp. Both morphology and abiotic data (temperature, waves and wind) were standardised using the *decostand* function in the *vegan* software package; morphology data were used as response variables and the abiotic data as explanatory variables. To determine the explanatory variables that best describe patterns in the response data, a full RDA was performed using a complete set of explanatory variables. Forward selection was then used to reduce the number of explanatory variables as well as prevent the inflation of overall type I error. To further improve the model, pairwise coefficients and Variance Inflation Factor (VIF) were calculated to identify variables with high multicollinearity. The computation of the parsimonious RDA was followed by permutation tests of the adjusted *R*2 to assess significance of constraints.
